Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-31 notes/privacy-proof/main.tex
update codes for experiments and fix typos in proof

\section{$\gamma$ -Smooth Sensitivity}
\label{sec_mechs}
$S_\beta(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:

\begin{equation}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma + d(\dataobs,\dataobs')} \bigg \},
\end{equation}
where $d$ is the Hamming distance between two data sets, and $\gamma = 1$.

\section{Mechanism Proposition}
\label{sec_mechs}
Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set:
\[
  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
\]
where $\Delta\alpha$ is as defined in Section\ref{sec_background}.
Notice that $\candidateset$ has $n + 1$ elements, and
the Bayesian Inference process will produce an element from $\candidateset$
that we denote by $\bysinfer(\dataobs)$ -- we don't explicitely
parametrize the result by the prior, which from now on we consider
fixed and we denote it by $\bprior$.

\subsection{$\hexpmech$: Smoothed Hellinger Distance Based Exponential Mechanism}
\label{subsec_hexpmech}

\begin{definition}
\label{def_smoo}
The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\nomalizer{\dataobs}}.
\end{equation*}
where $S_\beta(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:

\begin{equation}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma + d(\dataobs,\dataobs')} \bigg \},
\end{equation}
where $d$ is the Hamming distance between two datasets, and $\gamma = 0.5$.
\end{definition}

This mechanism is based on the basic exponential mechanism
\cite{talwar}, with $\candidateset$ as the range and
$\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
that in this mechanism we don't calibrate the noise w.r.t. to the
global sensitivity of the scoring function but w.r.t. to the smooth
sensitivity $S(\dataobs)$ -- defined by \cite{nissim2007smooth}-- of
$\hellinger(\bysinfer(\dataobs), \cdot)$.

$\gamma = \gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$ to
be determined later, and where $LS(\dataobs')$ denotes the local
sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$,
of the scoring function used in our mechanism.

This mechanism also extends to the Dirichlet-multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
\[
  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
\]
and by replacing the $\candidateset$ with set of posterior Dirichlet
distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
in (\ref{eq:smooth}) will be computed by letting $\dataobs'$ range
over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
will denote by $\hexpmechd$ the mechanism for the
Dirichlet-multinomial system.

By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private, where $\delta = \frac{e^{\frac{\epsilon}{2}} \delta'}{2}$. (or $\gamma = \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$ when generalized to Dirichlet-multinomial System)

@@

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
  \begin{equation*}
  \begin{split}
  & \leq \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot exp\big( \frac{\epsilon}{2} \big) \\
  & = exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)\\
  \end{split}
  \end{equation*}

  \begin{equation*}
  \begin{split}
  & = exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{2}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

>>>>

\section{$\gamma$-Smooth Sensitivity}
\label{sec_mechs}

\begin{definition}

$S(\dataobs)$ is the $\gamma -$smooth sensitivity of data set $\dataobs$, s.t. for any $\adj{\dataobs}{\dataobs'}$:

\begin{equation}
\label{eq_gamma_smooth}
|\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')}| \leq \gamma.
\end{equation}
\end{definition}

\begin{thm}
\label{thm_gamma_smooth}
$S_\beta(\dataobs)$ is $\gamma -$smooth sensitivity for $\hellinger(\bysinfer(\dataobs),-)$ if it is calculated by:
\begin{equation}
  \label{eq_smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma + d(\dataobs,\dataobs')} \bigg \},
\end{equation}
where $d$ is the Hamming distance between two data sets.
\end{thm}

\begin{proof}
of Theorem. \ref{thm_gamma_smooth}.

\end{proof}

\section{$\hexpmech$: Smoothed Hellinger Distance Based Exponential Mechanism}
\label{sec_mechs}
Given a prior distribution $\bprior = \betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set:
\[
  \candidateset\dataobs \equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
\]
where $\Delta\alpha$ is as defined in Section\ref{sec_background}.
Notice that $\candidateset{\dataobs}$ has $n + 1$ elements, and
the Bayesian Inference process will produce an element from $\candidateset{\dataobs}$
that we denote by $\bysinfer(\dataobs)$ -- we don't explicitely
parametrize the result by the prior, which from now on we consider
fixed and we denote it by $\bprior$.

\begin{definition}
\label{def_smoo}
The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset\dataobs$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\nomalizer{\dataobs}}.
\end{equation*}
where $S_\beta(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by Theorem \ref{thm_gamma_smooth}.
\end{definition}

@@

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
  \begin{equation*}
  \begin{split}
  & \leq \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot exp\big( \frac{\epsilon}{2} \big) \\
  & = exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)\\
  & = exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{2}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}
